---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bibsearch

<!-- badges: start -->
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/CorradoLanera/bibsearch?branch=master&svg=true)](https://ci.appveyor.com/project/CorradoLanera/bibsearch)
[![Travis build status](https://travis-ci.org/CorradoLanera/bibsearch.svg?branch=master)](https://travis-ci.org/CorradoLanera/bibsearch)
[![Codecov test coverage](https://codecov.io/gh/CorradoLanera/bibsearch/branch/master/graph/badge.svg)](https://codecov.io/gh/CorradoLanera/bibsearch?branch=master)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![CRAN status](https://www.r-pkg.org/badges/version/bibsearch)](https://CRAN.R-project.org/package=bibsearch)
<!-- badges: end -->

The goal of bibsearch is to provide simple to use wrappers to API of
multiple bibliographic search engines and database (e.g., Scopus,
PubMed), with the specific aim of create shareable files (e.g., bibTeX,
RIS).

## Installation

You can install the development version of **bibsearch** from
[GitHub](https://github.com) with:

``` r
# install.packages("devtools")
devtools::install_github("CorradoLanera/bibsearch")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval=FALSE}
library(bibsearch)

search_on_pubmed("(machine learning) AND lanera[Author]") %>% 
    write_bibliography()

search_on_scopus("(machine learning) AND lanera[Author]") %>% 
    write_bibliography()

```

## Code of Conduct
Please note that the **bibsearch** project is released with a
[Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
